\cvsection{ Hardware and IDE's}
    \begin{itemize}
    \item Version Control-GIT, Bitbucket.
    \item HARDWARES :Arduino Uno ,Rasberry Pi ,MCS 8051, ESP 32, EMG Sensors.
     \item  IDE : Visual Studio Code, Pycharm ,Sublime text ,Arduino IDE, Jupyter Notebook and Anaconda.
     \item Libraries:Pandas,Numpy,Keras,
     Tensorflow,Seaborn,
     Matplotlib,Scikit learn.
\end{itemize}

\cvsection{Languages}

\cvskill{English}{5}
% \divider



\cvskill{Hindi}{5}
% \divider

\cvskill{German}{2}
% \divider



\divider

\cvsection{Internships}


\cvevent{Image Processing Intern}{Arohi Software Solutions Pvt. Ltd}{Nov 2017--Jan 2018}{India }
\begin{itemize}
\item Worked in creating inputs for a machine learning algorithm.

\end{itemize}





\cvsection{PUBLICATIONS}
\begin{itemize}
    \item Karol Adnan Mushtaq Ali, 'Mobile Hand-off using Wireless CAN protocol: An approach to reduce call drops', International
Research Journal of Engineering and Technology,March 2019, Issue 3, Volume 6.
    \item Karol Adnan Mushtaq Ali, 'Plant Disease Detection using CNN and Remedy', International Journal of Advanced Research in
Electrical, Electronics and Instrumentation Engineering,March 2019,Issue 3,Volume 8.


   
\end{itemize}


\cvsection{Honors \& Awards}
\begin{itemize}
    \item Recieved the prestigious Tata scholarship for outstanding overall performance.
    \item Awarded the e-fellows.net scholarship in May 2019-Stuttgart,Germany.
    \item Participated in Smart India Hackathon and Rajasthan hackathon , which are non stop coding competitions by Government of India.
    \item Recieved well recognition in National Level Project  Competition. Networks.
    \item  Project was selected amongst the Top 5 project of the department by the College
    \item Completed training and courses in various workshops titled " Networking and Hardware" ," Internet of Things "," Mobile Making Workshop" etc.
    
\end{itemize}


\dividers